\pdfcompresslevel=0
\pdfobjcompresslevel=0
\documentclass[a4paper]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{textcomp}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[left=0.5in,right=0.5in,bottom=0.5in,top=0.5in]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}

\textheight=10in
\pagestyle{empty}
\raggedright

\definecolor{deeppurple}{RGB}{102, 0, 153}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{3pt} \textcolor{deeppurple}{\textsc{#1}}}
    \vspace*{-12pt} \\
    \hspace*{-18pt} \textcolor{deeppurple}{\hrulefill} \\
}

% Adjust list parameters for itemize environment
\addtolength{\leftmargini}{-1em}
\addtolength{\leftmarginii}{-1em}

\begin{document}
\vspace{-40pt}

%==== Profile ====%
\begin{center}
    {\fontsize{36}{36}\selectfont \textcolor{deeppurple}{Forest Welch}} \\ % Adjusted font size and color
    \vspace{10pt} % Add space between name and contact info
    \small San Francisco, CA $\cdot$ \href{mailto:forest.r.welch@gmail.com}{\underline{forest.r.welch@gmail.com}} $\cdot$ (415) 375-5162 $\cdot$ \href{https://linkedin.com/in/forestrwelch}{\underline{linkedin.com/in/forestrwelch}} $\cdot$ \href{https://github.com/nwelchr}{\underline{github.com/nwelchr}} % Reduced font size for contact information
\end{center}

\vspace{10pt}

Fullstack Software Engineer with over 4 years of experience in React and Node.js. My strong communication skills enable me to collaborate effectively across disciplines and deliver high-quality solutions. I am committed to continuous growth and have a passion for using technology to make a positive impact, particularly in the mental health sector.

%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{BuildVision} \hfill San Francisco, CA\\
\textit{Software Engineer (Contract)} \hfill November 2023 - April 2024\\
\vspace{-1mm}
\begin{itemize} \itemsep .5pt
    \item Spearheaded Next.js UI development for admin tools and customer views as BuildVision's second engineer.
    \item Leveraged RTK Query's cache tags to optimize data management and API interactions, building reusable Table and Pagination components with result caching, search filters, and inline editing.
    \item Established a comprehensive design system using NextUI, creating reusable components and standardizing styles, such as a file folder viewer with recursive nesting and state management.
\end{itemize}

\textbf{Autodesk (Formerly BuildingConnected)} \hfill San Francisco, CA\\
\textit{Software Engineer} \hfill August 2018 - January 2022\\
\vspace{-1mm}
\begin{itemize} \itemsep .5pt
    \item Authored an org-wide React UI component library, reducing library size by \textasciitilde{}30\% and doubling functionality.
    \begin{itemize} \itemsep .5pt
        \item Unified disparate component libraries and JSS-in-CSS with styled-components to simplify UI development.
        \item Developed common components including action menus, tables, and flyouts.
        \item Documented props, and usage, and design principles, accessible at \href{https://design.buildingconnected.com/}{\underline{design.buildingconnected.com}}.
        \end{itemize}
    \item Led a localization and internationalization initiative, doubling the user base by expanding into Oceania.
    \begin{itemize} \itemsep .5pt
            \item Implemented a centralized translation system using react-i18next, with hierarchical locale determination using user settings, browser language, HTTP headers, and geolocation.
            \item Injected locale into server-side HTML templates for email and printer services, ensuring consistent localization.  
        \end{itemize}
    \item Rebuilt internal tools from the ground up, saving the Customer Success team 20 hours per week.
    \begin{itemize} \itemsep .5pt
            \item Converted UI from Angular to React for better performance and added enhanced search and company merging.
            \item Fixed a critical date picker bug, saving several million dollars by preventing contract expiration issues.
        \end{itemize}
    \item Led the estimated cost feature development, empowering contractors' decisions (used >5000 times weekly).
    \begin{itemize} \itemsep .5pt
            \item Crafted a comprehensive design document detailing approaches, requirements, and implementation plans.
            \item Developed a reusable EstimatedCost component with Redux for real-time updates and implemented memoization with reselect for performance optimization.  
        \end{itemize}
    \item Mentored two entry-level engineers and an intern, providing structured onboarding sessions, conducting pair programming, and offering detailed, constructive feedback during PR reviews.
    \item Improved team morale and mitigated burnout during COVID by organizing and hosting bi-weekly yoga and meditation Zoom calls, along with weekly pair programming and gaming sessions.
    \item Managed the frontend interview process, conducting interviews and assisting candidates during onsites. Key contributor to the successful hire of 5 engineers and 2 interns, and launched our first satellite office in Toronto.
\end{itemize}

%==== Education ====%
\header{Education}
\textbf{University of Pennsylvania}\hfill Philadelphia, PA\\
B.A. in Linguistics, minor in Deaf Studies \hfill 2012 - 2016\\
\vspace{2mm}
\textbf{App Academy}\hfill San Francisco, CA\\
Fullstack Engineering Certificate \hfill 2018\\
\vspace{2mm}

%==== Skills ====%
\header{Skills}
\vspace{1mm}
\begin{tabular}{ l p{5.2in} }
    \textbf{Proficient:} & JavaScript, React, Next.js, Redux, Node.js, MongoDB, Git, CircleCI \\
    \textbf{Familiar:}   & Typescript, React Native, Angular, PostgreSQL, Docker, Heroku, AWS, Elastic Cloud, Redis, Mongoose, GraphQL, Jest, Cypress, Ruby on Rails, Webpack, jQuery \\
\end{tabular}

\end{document}